A novel 1000\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers

### 2018-02-04 article.tex
基本修改完成 提交杨涛老师

\documentclass[preprint,12pt]{elsarticle}
\usepackage{caption} 
%\renewcommand{\captionlabeldelim}{.}
\usepackage{color}%临时添加,
\usepackage{amssymb,hyperref,booktabs,multirow,multicol,ifthen}
\usepackage{enumerate}
\usepackage{nomencl}
\usepackage{float}
\usepackage{graphics}
\usepackage{framed}

@@

% \usepackage{graphicx}%插入图片

% \usepackage{amssymb}%数学符号

% \usepackage{amsthm}%数学定理

 \usepackage{amsmath}%数学公式、矩阵、积分求和等

% \usepackage{lineno}%显示行号

% \usepackage{txfonts}%默认字体times new roman

% \usepackage{enumitem}%项目编号

% \usepackage{multirow}%多行合并

% \usepackage{caption}%改变图表标题

% \usepackage{array}%调用公式宏包的命令应放在调用宏包命令之前，也能控制表格

% \usepackage{booktabs}%调整表格线与上下内容的间隔

% \usepackage{longtable}%调用跨页表格

\usepackage{bm}%数学字体加粗

% \usepackage{setspace}%调整一段文字的行间距

% \usepackage{natbib}%参考文献管理包​
% \biboptions{sort&compress}%参考文献可以压缩显示比例​

% \allowdisplaybreaks[4]%允许公式跨页

\captionsetup[figure]{font=small,labelfont=bf,labelsep=period}%修改标题文字格式

\renewcommand{\figurename}{Fig.}%修改标题样式

%\newcommand{\tabincell}[2]{}%让表格内容自动换行，但仍然需要用到换行\\

@@

\begin{abstract}%修改到300字以内
Double-reheat ultra-supercritical (USC) unit has received extensive attention for its high efficiency and energy-saving effect.
The optimal design of its thermal system is still under study.
Herein, an optimized system for reasonable fluid heat transfer temperature matching and higher efficiency was proposed.
The novel system used turbine extractions as heat sources of air preheaters and low-pressure economizers to absorb economizer outlet flue gas’ heat, which realized the join optimization of air preheat process and regenerative system.
Models were built to compare energetic performance of the novel system and reference system.
In addition, thermodynamic analyses under partial load operation conditions was conducted. 
Exergy analysis method was used to identify exergy destruction changes of transformed parts and analyze the cause of the change.
Result shows the novel system can largely decrease exergy destruction rate of air preheat process and improve the system's thermal performance.
Furthermore, the novel system increases the temperature of secondary air and reduces the overall superheat degree of several extractions.
Theoretically, the novel system with a overall exergy efficiency of 48.73\%  and reduces the SCE consumption by nearly 5.5\,g/kWh under THA load when the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
Moreover, the novel system can still has advantages in coal saving under partial load condition.

@@

\printnomenclature[1.5cm]{}

@@

Due to arrangement of boiler heating surface and design of regenerative system belong to deferent research area, researches concentrate more on the optimization of these two systems respectively, and ignored the joint optimization of boiler tail flue heating surface and regenerative system to achieve energy cascade utilization and improve system efficiency.
To reduce both systems' exergy loses, a theoretical optimization design of cascaded utilization of energy for a 1000\,MW double reheat USC unit (novel system) is proposed. Variations and energy saving effects of a double reheat ultra-supercritical thermal system (reference system) and the novel system are analyzed to evaluate their performance. 
\section{System optimization of double reheat USC system}
\label{sec2:system intro}
\subsection{Reference system on operation} % (fold)
\label{sub2:ref intro}
A typical coal-fired double reheat USC power plant in operation is chosen as the reference unit.
The parameter settings that maximize continuous power are 310\,bar/600$^\circ$C for the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of the single reheat steam pressure to the main steam pressure, and 33\% for the proportion of the double reheat steam pressure to the single reheat steam pressure[6].
The output power of the double reheat unit under the design condition is 1000 MW.
The unit consists of one super high pressure turbine (VHP), one high pressure turbine (HP), one intermediate pressure turbine (IP), and two low pressure turbines (LP).
10-stage regenerative system with four high pressure regenerative heaters (HRH), five low pressure regenerative heaters (LRH), and one deaerator (DEA) are adopted.
Besides two additional outer steam coolers (AOC1, AOC2) are used to cool two extractions due to its high super-heating degree. The exhaust steam pressure of the steam turbine is set 4.5\,kPa. The simplified schematic of the unit is presented in Fig~\ref{fig:reference_system}.

\begin{figure}[htbp]
\centering
\includegraphics[width=1\textwidth]{fig/reference_system}
\caption{Schematic of the reference system} 
\label{fig:reference_system}
\end{figure}
%从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
Furnace layout shown in Fig~\ref{fig:boiler_surface}, the boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature first reheater (Csf), cold segment of high-temperature second reheater (Csf), High temperature super-heater (Hts), hot segment of high-temperature first reheater (Hsf), hot segment of high-temperature second reheater (Hss).
After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue. The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizers.
APH is arranged in vertical shaft.

From the arrangement of heating surfaces of boiler, it can be seen that most heating surfaces of boiler is arranged in the furnace, while the horizontal flue and vertical shaft are only equipped with air preheating equipment. So the boiler can be divided into two parts: the boiler achieving heat absorption of water/steam in the furnace, and the APH to complete the air preheating.
\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/boiler_surface}
\caption{Boiler internal heat exchangers layout} 
\label{fig:boiler_surface}
\end{figure}

@@

\begin{table}[htbp]
\caption{Fluid parameters of heat exchangers and air preheater}
\label{tab:reheater parameter}
\centering
\begin{tabular}{llll}
\toprule 
\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{3.2cm}{Cold fluid temperature ($^\circ$C)}&\multirow{2}{2.2cm}{LMTD ($^\circ$C)}\tabularnewline
&&&\tabularnewline
\midrule
APH  &  376.00 	& 23.00  & 72.4\tabularnewline
AOC1 &   526.56 & 304.51 & 69.75\tabularnewline
AOC2 &  527.48 	& 304.51 & 60.81\tabularnewline
HRH1 &   417.07 & 273.62 & 10.64\tabularnewline
HRH2 &   314.53 & 240.73 & 10.77\tabularnewline
HRH3 &   434.54 & 205.89 & 12.68\tabularnewline
HRH4 &   316.51 & 186.48 & 6.88\tabularnewline
LRH6 &  394.01 	& 140.46 & 13.19\tabularnewline
LRH7 &   313.17 & 104.49 & 15.87\tabularnewline
LRH8 &   191.84 & 82.42  & 9.82\tabularnewline
LRH9 &   116.61 & 59.25  & 10.03\tabularnewline
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:reheater parameter} gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
For the APH, the temperature of flue gas at the inlet is 376$^\circ$C under design condition, while the temperature of the air to be heated by the flue is 23$^\circ$C.
The logarithm mean temperature difference (LMTD) of the APH is calculated to be 72$^\circ$C.
Compared with the air preheater, the regenerative heaters have lower LMTD.
However, it is found that the temperature difference between the hot and cold stream at the inlet high temperature regenerative heaters is also relatively large, which causes irreversible loss. 
To reduce the superheat degree of the 2nd and 4th extractions and to heat feedwater, two additional outer steam coolers are installed.
Results show that the inlet temperature difference of HRH2 and HRH4 is greatly reduced, and the exergy efficiency is improved correspondingly.
However, the inlet temperature difference between the cold and hot stream of other high temperature regenerative heaters remains very high.
Moreover, because of the material restriction of the water wall, the temperature of feedwater at the inlet of boiler is restricted to 315$^\circ$C. 
In the reference system, the first extraction has to be throttled to ensure the temperature of feedwater not exceeding the restriction.
The pressure of the first extraction is throttled from 106.70 bar to 88.56 bar, and the temperature is decreased from 425.60$^\circ$C to 413.77$^\circ$C. The throttling of the first extraction will certainly cause extra irreversible loss.

\subsection{Proposal of a novel system with EAPH and LPE}
\label{sub2:prop novel sys}
%添加为什么进行这种设计的解释，为什么设置LPE AOC APH的级数

To reduce the energy loss caused by APH, a novel system is proposed, in which air is not heated by flue gas in the conventional air preheater, and 8 turbine-extraction-heated air preheaters (EAPH1-EAPH8) are adopted.
The  layout of the optimization system is presented in Fig.~\ref{fig:novel_system}.

The new air preheater is similar with regenerative heaters in function.
As shown in Fig.~\ref{fig:extraction_heat_APH} the extracted steam is sent to the regenerative heater to heat the condensate or feedwater, and then the drainage from the air preheater joins with that of corresponding regenerative heater.
It should be mentioned that not all the extractions are available for air heating.
The last two stage extractions' pressure are much lower than barometric pressure which makes it extremely difficult to maintain such low pressure environment inside the heat exchangers, and APH8 shall be shut down under low load for the same reason.
Besides, to reduce the superheat degree of extractions entering the heat exchangers and to improve the air temperature, four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of APH1.
Since extractions from the 2nd to the 5th have great superheat degree, they are sent to AOCs in the order of temperature level.
For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air APH2 to heat the water and air respectively.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.3\textwidth]{fig/extraction_heat_APH}%extraction_heat_APH
\caption{Process flow diagram of RH and APH} 
\label{fig:extraction_heat_APH}
\end{figure}

Cause removing of the APH originally installed in the vertical shaft, the flue gas's heat needs to be absorbed by other means.
As shown in Fig~\ref{fig:novel_system}, the flue gas at the outlet of economizer is utilized to heat the condensate and feed water by four LPEs, which are paralleled to HRH2, HRH4, LRH6, and LRH8 respectively. 
Part of the condensate and feed water at the inlet of regenerative heater are sent to the LPE, then the heated water join with the main feedwater/condensate. 
Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE is set 95$^\circ$C. 
The temperature of heated water from LPE is set little higher than the feedwater from the corresponding regenerative heater.%

@@

\subsection{Model establish method and main assumption}
\label{ssub3:modle description}
%对模型中如何基于现有系统进行的改造，和哪些数据不发生变化进行说明
%添加模型中基本部件的特性 添加个表格
In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional.
EBSILON is a power plant simulation tool which can calculate thermodynamic quantities and widely used in power plant system model establishment and analysis~\cite{Li2015Integrated,Yao2017Multi}. 
The simulation model gives the detailed data with high degree of reliability to calculate the thermodynamic state.
While use this software simulating systems, main equipments work flow parameters and some basic properties need to be settled.
Cause designed based on the reference system, the novel system's main input parameters(such as live steam parameters, fist/second reheat steam parameters and turbine extractions parameters) keeps the same as reference system, which can be find in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
Based on the practice, the upper temperature differences of novel systems' LPE, AOC and EAPH are settled to 30℃, 20℃ and 5℃. 
And other main components model details are give in Table~\ref{table:model_details}.

\begin{table}
\caption{Model details of main components}
\label{table:model_details}
\begin{centering}
\begin{tabular}{ll}
\toprule 
Components 				& Model details\tabularnewline
\midrule
Boiler         			& Economizer out let flu temperature =376\textcelsius ;\tabularnewline
 						& Slag temperature =850\textcelsius ;\tabularnewline
 						& Combustion efficiency =0.99.\tabularnewline
Turbine 				& Isentropic efficiencies are from 0.83 to 0.93, \tabularnewline
 						& calculated from thermal equilibrium diagram.\tabularnewline
Condenser 				& Upper terminal temperature difference=5\textcelsius .\tabularnewline
Regenerative reheats 	& Upper terminal temperature differences are from -1.7\textcelsius{}to 2.2\textcelsius , \tabularnewline
 						& calculated from thermal equilibrium diagram.\tabularnewline
\bottomrule
\end{tabular}
\par\end{centering}
\end{table}

@@

\subsection{Thermodynamic metric} %(fold)
\label{ssub3:analsys method} 
%为了能够对优化系统与参考系统进行评估，揭示系统优化的内在机理，本文引入热力学第二定律的分析方法即用分析方法。
Exergy analysis, is adopted to reveal the location, the magnitude and the sources of thermodynamic inefficiencies of the unit.
Usually, exergy destruction and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
The general exergy balance of component can be expressed in the following form:
\begin{equation}
\label{equation:1}
\dot{I}=\sum\dot{X}{}_{in}-\sum\dot{X}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
\end{equation}

Exergy efficiency can be calculated in the following form:
\begin{equation}
\label{equation:2}
\eta=\frac{\dot{X}{}_{earned}}{\dot{X}{}_{cost}}
\end{equation}
For different equipment under stable operating conditions, equation~\ref{equation:1}, ~\ref{equation:2} have different forms as shown in Table~\ref{tab:exergy equation}~\cite{Aljundi2009Energy}

\begin{table}
\caption{Exergy analysis equations for plant components}
\label{tab:exergy equation}
\centering
\begin{tabular}{lll}
\toprule 
 & Exergy destruction rate  & Exergy efficiency\tabularnewline
\midrule
Boiler & $\dot{I}_{boiler}=\dot{X}{}_{fuel}+\dot{X}{}_{in}-\dot{X}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{X}{}_{out}-\dot{X}{}_{in}}{\dot{X}{}_{fuel}}$\tabularnewline
Pump & $\dot{I}_{pump}=\dot{X}{}_{in}-\dot{X}{}_{out}+\dot{W}{}_{pump}$ & $\eta_{\uppercase\expandafter{\romannumeral2},pump}=1-\frac{\dot{I}_{pump}}{\dot{W}{}_{pump}}$\tabularnewline
Heater & $\dot{I}_{heater}=\dot{X}{}_{in}-\dot{X}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},heater}=1-\frac{\dot{I}_{heater}}{\dot{X}{}_{in}}$\tabularnewline
Turbine & $\dot{I}_{turbine}=\dot{X}{}_{in}-\dot{X}{}_{out}-\dot{W}{}_{el}$ & $\eta_{\uppercase\expandafter{\romannumeral2},turbine}=1-\frac{\dot{I}_{turbine}}{\dot{X}{}_{in}-\dot{X}{}_{out}}$\tabularnewline
Condenser & $\dot{I}_{condenser}=\dot{X}{}_{in}-\dot{X}{}_{out}+\dot{W}{}_{p}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{X}{}_{out}}{\dot{X}{}_{in}+\dot{W}{}_{p}}$\tabularnewline
Cycle &$\dot{I}_{total}=\dot{X}{}_{fuel}-\dot{W}{}_{net,out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},total}=\frac{\dot{W}{}_{net,out}}{\dot{X}{}_{fuel}}$\tabularnewline
\bottomrule
\end{tabular}
\end{table}

@@

\begin{equation}{}
\label{equation:3}
x=h-h_{0}-T_{0}\left(s-s_{0}\right)
\end{equation}
Then the total exergy rate associated with ﬂuid stream becomes:
\begin{equation}
\dot{X}=\dot{m}x=\dot{m}\left[h-h_{0}-T_{0}\left(s-s_{0}\right)\right]{}
\end{equation}
The fuel specific exergy calculate method~\cite{Yan2016The} can be expressed as.
\begin{equation}
x_{fuel}=LHV\left(1.0064+0.1519\frac{H}{C}+0.0616\frac{O}{C}+0.0429\frac{N}{C}\right)
\end{equation}
Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fractions of carbon, hydrogen, oxygen, nitrogen by element analysis.
More details of power plant equipments' exergy  efficiency calculation can be found in Ref.~\cite{G2016Exergy}

In order to clearly analyze the effect of system optimization, this paper divides the double-reheat USC system into four main subsystems and a sum of all other equipments, valves and pips named "other".
The four main subsystems are : boiler with out APH, turbines, air preheat subsystem and regenerative subsystem.
The equations mentioned above can also be used into exergy analysis of these four main subsystems.
For the "other" part, this paper used counter balance analysis method to calculate its exergy destruction rate, which means subtract the share of the four main subsystems from the total exergy destruction.
The exergy destruction rate can be calculated by using equation as follows:

@@

\section{Thermodynamic performance evaluation} % (fold)
\label{sub:Thermodynamic_evaluation}
%对word版本的分布进行了较大的改动，需要继续调节
\subsection{Thermodynamic comparison in design condition}
\label{ssub:desing_compare}
%表四
The comparison of thermal dynamic performance between these two systems is given in Table~\ref{table:thermal performance compare}. 
Under design condition, the novel system brings an improvement of net generating power by 11.02 MW, and reduces SCE consumption by 5.5\,g/kWh.
The power generation efficiency reaches 48.73\%, 1.04\% higher then that of reference system.
Meanwhile, the exergy efficiency of novel system is 1.01\% higher, showing good exergy-saving effect.

>>>>

\documentclass[preprint,12pt]{elsarticle}
\usepackage{caption} 
\usepackage{color}%临时添加,
\usepackage{amssymb,hyperref,booktabs,multirow,multicol,ifthen}
\usepackage{enumerate}
\usepackage{nomencl}
\usepackage{float}
\usepackage{graphics}
\usepackage{framed}

@@

 \usepackage{amsmath}%

 \usepackage{lineno}%

\usepackage{bm}%

\captionsetup[figure]{font=small,labelfont=bf,labelsep=period}%

\renewcommand{\figurename}{Fig.}%

@@

\begin{abstract}%修改到300字以内
Double-reheat ultra-supercritical (USC) unit has received extensive attention for its high efficiency and energy-saving effect.
The optimal design of its thermal system is still under study.
Herein, an optimized system for reasonable fluid heat transfer temperature matching and higher efficiency was proposed.
The novel system used turbine extractions as heat sources of air preheaters and low-pressure economizers to absorb economizer outlet flue gas’ heat, which realized the join optimization of air preheat process and regenerative system.
Models were built to compare energetic performance of the novel system and reference system.
In addition, thermodynamic analyses under partial load operation conditions was conducted. 
Exergy analysis method was used to identify exergy destruction changes of transformed parts and analyze the cause of the change.
Result shows the novel system can largely decrease exergy destruction rate of air preheat process and improve the system's thermal performance.
Furthermore, the novel system increases the temperature of secondary air and reduces the overall superheat degree of several extractions.
Theoretically, the novel system with a overall exergy efficiency of 48.73\%  and reduces the SCE consumption by nearly 5.5\,g/kWh under THA load when the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
Moreover, the novel system can still has advantages in coal saving under partial load condition.
Results indicate that the novel system could improves the performance of double-reheat USC unit and may provide a theoretical basis for its optimization.

@@

\begin{multicols}{2}
\printnomenclature[1.5cm]{}
\end{multicols}

@@

Due to  boiler design and thermal system design belong to deferent research area, boiler has been studied as a whole and ignored the joint optimization of boiler heat transfer process and regenerative process.

In this paper, a novel system based on a 1000\,MW double reheat USC reference system  is proposed to realize boiler and regenerative system energy cascade utilization. 
The novel system realized reasonable temperature matching of flue gas, air, extraction steam and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and LPEs.
Specifically, the main works of this study include: (1)Modeling the novel system and reference system with EBSILON® Professional; (2) Using exergy analysis to compare both systems' exergy efficiency , exergy destruction distribution and subsystems performance change;(3) Analyzing both systems' thermal performance under off-design conditions.

\section{System optimization of double reheat USC system}
\label{sec2:system intro}
\subsection{Reference system on operation} % (fold)
\label{sub2:ref intro}
A typical coal-fired double reheat USC power plant in operation is chosen as the reference unit.
The parameter settings at maximize continuous power are 310\,bar/600$^\circ$C for the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of the single reheat steam pressure to the main steam pressure, and 33\% for the proportion of the double reheat steam pressure to the single reheat steam pressure~\cite{Zhao2017Exergy}.
The output power of the reference system under the design condition is 1000 MW.
The unit consists of one super high pressure cylinder (VHP), one high pressure cylinder (HP), one intermediate pressure cylinder (IP), and two low pressure cylinders (LPs).
Regenerative system with four high pressure regenerative heaters (HRHs), five low pressure regenerative heaters (LRHs), and one deaerator (DEA) are adopted.
Besides, two additional outer steam coolers (AOC1, AOC2) are used to cool two extractions due to its high super-heating degree. The exhaust steam pressure of the steam turbine is set 4.5\,kPa. The simplified schematic of it is presented in Fig~\ref{fig:reference_system}.

\begin{figure}[htbp]
\centering
\includegraphics[width=1\textwidth]{fig/reference_system}
\caption{Schematic of the reference system} 
\label{fig:reference_system}
\end{figure}
%从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
The system's boiler heat transfer surfaces arrangement is shown in Fig~\ref{fig:boiler_surface}. 
The boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature first reheater (Csf), cold segment of high-temperature second reheater (Css), High temperature super-heater (Hts), hot segment of high-temperature first reheater (Hsf), hot segment of high-temperature second reheater (Hss).
After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue.
The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizer (Feco).
The back duct arranges low-temperature second reheater (Ltsr) and the back-duct economizer (Beco).
(air preheater)APH is arranged in vertical shaft.

From the arrangement of heating transfer surfaces, the boiler can be divided into two parts: the part achieving heat absorption of water/steam process in the furnace, and the APH to complete the air preheat process.
It can be seen that most heating surfaces of boiler is arranged in the furnace, while the horizontal flue and vertical shaft are only equipped with APH.
So the horizontal flue and vertical shaft have sufficient space to install other equipments.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.9\textwidth]{fig/boiler_surface.png}
\caption{Boiler heat transfer surfaces layout} 
\label{fig:boiler_surface}
\end{figure}

@@

Table~\ref{tab:reheater parameter} gives the temperature profiles of regenerative heaters and the air preheater, revealing their energy match level.
For the APH, the temperature of flue gas at the inlet is 376$^\circ$C under, while the temperature of the air to be heated by the flue is 23$^\circ$C.
The logarithm mean temperature difference (LMTD) of the APH is calculated to be 72$^\circ$C.
Compared with the air preheater, the regenerative heaters have much lower LMTD from 6.88$^\circ$C-15.87$^\circ$C.
According to the second law of thermodynamics, the bigger the temperature difference the greater the irreversible loss.
So it needs to optimize the air preheat process to reduce energy loss of the system.
AOC1 and AOC2 face the same problem of high LMTD compared with RHs.
It's better to find a way to make double reheat USC system's high temperature extractions a reasonable arrangement.

\begin{table}[htbp]
\caption{Fluid parameters of regenerative heaters and air preheater}
\label{tab:reheater parameter}
\centering
\begin{tabular}{llll}
\toprule 
\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{3.2cm}{Cold fluid temperature ($^\circ$C)}&\multirow{2}{2.2cm}{LMTD ($^\circ$C)}\tabularnewline
&&&\tabularnewline
\midrule
APH  &  376.00 	& 23.00  & 72.4\tabularnewline
AOC1 &   526.56 & 304.51 & 69.75\tabularnewline
AOC2 &  527.48 	& 304.51 & 60.81\tabularnewline
HRH1 &   417.07 & 273.62 & 10.64\tabularnewline
HRH2 &   314.53 & 240.73 & 10.77\tabularnewline
HRH3 &   434.54 & 205.89 & 12.68\tabularnewline
HRH4 &   316.51 & 186.48 & 6.88\tabularnewline
LRH6 &  394.01 	& 140.46 & 13.19\tabularnewline
LRH7 &   313.17 & 104.49 & 15.87\tabularnewline
LRH8 &   191.84 & 82.42  & 9.82\tabularnewline
LRH9 &   116.61 & 59.25  & 10.03\tabularnewline
\bottomrule
\end{tabular}
\end{table}

\subsection{Proposal of a novel system with EAPHs and LPEs}
\label{sub2:prop novel sys}

To reduce the energy loss caused by APH, a novel system is proposed, in which air is not heated by flue gas in the conventional air preheater, but 8 turbine-extraction-heated air preheaters (EAPH1-EAPH8).
The layout of the optimization system is presented in Fig.~\ref{fig:novel_system}.

As shown in Fig.~\ref{fig:extraction_heat_APH}, the extracted steam divides into two parts, one is sent to the regenerative heater to heat the condensate or feedwater and the other one is sent to corresponding EAPH to heat air.
The drainage from the air preheater joins with that of corresponding regenerative heater after finishing heat transfer .
Steam distribution ratio is determined according to EAPH upper terminal temperature difference settled in the system.
It should be mentioned that not all the extractions are available for air heating.
The last two stage extractions' pressure are much lower than barometric pressure which has a great risk of air leakage into the steam, and APH8 shall be shut down under low load for the same reason.

The AOCs in the reference system are designed to heat feedwater.
Although AOC inlet steam has a great supper heat degree, the small heat exchanged makes feedwater have little temperature rise.
So the LMTD is very high in AOCs.

To reduce rise AOCs' exergy efficiency and the superheat degree of extractions entering the heat exchangers, four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of EAPH1.
Air side outlet of EAPH1 will sent to boiler as secondary air, which has small mass quantity and lower heat capacity compared with feedwater. 
So the secondary air temperature can make a remarkable rise, and LMTD of AOCs can get down.
Extractions from the 2nd to the 5th have very high temperature and great superheat degree, they are sent to AOCs in the order of temperature level.
For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air EAPH2 to heat the water and air respectively.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.3\textwidth]{fig/extracion_heat_APH.png}%extraction_heat_APH
\caption{Process flow diagram of RH and EAPH} 
\label{fig:extraction_heat_APH}
\end{figure}

Cause removing of the APH originally installed in the vertical shaft, the flue gas's heat needs to be absorbed by other means.
As shown in Fig~\ref{fig:novel_system}, the flue gas at the outlet of economizer is utilized to heat the condensate and feed water by four LPEs, which are paralleled to HRH2, HRH4, LRH6, and LRH8 respectively. 
Part of the condensate and feed water at the inlet of regenerative heater are sent to the LPE, then the heated water join with corresponding regenerative heater's outlet water. 
Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE can be set 95$^\circ$C.

@@

\subsection{Model establish method and main assumption}
\label{ssub3:modle description}
%对模型中如何基于现有系统进行的改造，和哪些数据不发生变化进行说明
%添加模型中基本部件的特性 添加个表格
In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional.
EBSILON is a power plant simulation tool which can calculate thermodynamic quantities and widely used in power plant system model establishment and analysis~\cite{Li2015Integrated,Yao2017Multi}. 
The simulation model gives the detailed data with high degree of reliability to calculate the thermodynamic state.
While use this software simulating systems, main equipments work flow parameters and some basic properties need to be settled.
Cause designed based on the reference system, the novel system's main input parameters(such as live steam parameters, fist/second reheat steam parameters and turbine extractions parameters) keeps the same as it, which can be find in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
Based on the practice, the upper temperature differences of novel systems' LPE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C and 5$^\circ$C. 
And other main components model details are give in Table~\ref{table:model_details}.

\begin{table}
\caption{Model details of main components}
\label{table:model_details}
\begin{centering}
\begin{tabular}{ll}
\toprule 
Components 				& Model details\tabularnewline
\midrule
Boiler         			& Economizer out let flue gas temperature =376\textcelsius ;\tabularnewline
 						& Slag temperature =850\textcelsius ;\tabularnewline
 						& Combustion efficiency = 0.99.\tabularnewline
Turbine 				& Isentropic efficiencies are from 0.83 to 0.93, \tabularnewline
 						& calculated from thermal equilibrium diagram.\tabularnewline
Condenser 				& Upper terminal temperature difference = 5\textcelsius .\tabularnewline
Regenerative reheats 	& Upper terminal temperature differences are from -1.7\textcelsius{}  \tabularnewline
 						& to 2.2\textcelsius ,calculated from thermal equilibrium diagram.\tabularnewline
\bottomrule
\end{tabular}
\par\end{centering}
\end{table}

@@

\subsection{Thermodynamic metric} %(fold)
\label{ssub3:analsys method} 
%为了能够对优化系统与参考系统进行评估，揭示系统优化的内在机理，本文引入热力学第二定律的分析方法即用分析方法。
Exergy analysis, is adopted to reveal the location, the magnitude and the sources of thermodynamic inefficiencies of the unit.
Usually, exergy destruction and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
The general exergy balance of component or system can be expressed in the following form:
\begin{equation}
\label{equation:1}
\dot{I}=\sum\dot{Ex}{}_{in}-\sum\dot{Ex}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
\end{equation}

Exergy efficiency can be calculated in the following form:
\begin{equation}
\label{equation:2}
\eta_{\uppercase\expandafter{\romannumeral2}}=\frac{\dot{Ex}{}_{earned}}{\dot{Ex}{}_{cost}}
\end{equation}
For different equipment under stable operating conditions, equation~\ref{equation:1}, ~\ref{equation:2} have different forms as shown in Table~\ref{tab:exergy equation}~\cite{Aljundi2009Energy}

\begin{table}
\caption{Exergy analysis equations for power plant components}
\label{tab:exergy equation}
\centering
\begin{tabular}{lll}
\toprule 
 & Exergy destruction rate  & Exergy efficiency\tabularnewline
\midrule
Boiler & $\dot{I}_{boiler}=\dot{Ex}{}_{fuel}+\dot{Ex}{}_{in}-\dot{Ex}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{Ex}{}_{out}-\dot{Ex}{}_{in}}{\dot{Ex}{}_{fuel}}$\tabularnewline
Pump & $\dot{I}_{pump}=\dot{Ex}{}_{in}-\dot{Ex}{}_{out}+\dot{W}{}_{pump}$ & $\eta_{\uppercase\expandafter{\romannumeral2},pump}=1-\frac{\dot{I}_{pump}}{\dot{W}{}_{pump}}$\tabularnewline
Heater & $\dot{I}_{heater}=\dot{Ex}{}_{in}-\dot{Ex}{}_{out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},heater}=1-\frac{\dot{I}_{heater}}{\dot{Ex}{}_{in}}$\tabularnewline
Turbine & $\dot{I}_{turbine}=\dot{Ex}{}_{in}-\dot{Ex}{}_{out}-\dot{W}{}_{el}$ & $\eta_{\uppercase\expandafter{\romannumeral2},turbine}=1-\frac{\dot{I}_{turbine}}{\dot{Ex}{}_{in}-\dot{Ex}{}_{out}}$\tabularnewline
Condenser & $\dot{I}_{condenser}=\dot{Ex}{}_{in}-\dot{Ex}{}_{out}+\dot{W}{}_{pump}$ & $\eta_{\uppercase\expandafter{\romannumeral2},boiler}=\frac{\dot{Ex}{}_{out}}{\dot{Ex}{}_{in}+\dot{W}{}_{pump}}$\tabularnewline
Cycle &$\dot{I}_{total}=\dot{Ex}{}_{fuel}-\dot{W}{}_{net,out}$ & $\eta_{\uppercase\expandafter{\romannumeral2},total}=\frac{\dot{W}{}_{net,out}}{\dot{Ex}{}_{fuel}}$\tabularnewline
\bottomrule
\end{tabular}
\end{table}

@@

\begin{equation}{}
\label{equation:3}
ex=h-h_{0}-T_{0}\left(s-s_{0}\right)
\end{equation}
Then the total exergy rate associated with ﬂuid stream becomes:
\begin{equation}
\dot{Ex}=\dot{m}x=\dot{m}\left[h-h_{0}-T_{0}\left(s-s_{0}\right)\right]{}
\end{equation}
The fuel specific exergy calculate method~\cite{Yan2016The} can be expressed as.
\begin{equation}
ex_{fuel}=LHV\left(1.0064+0.1519\frac{H}{C}+0.0616\frac{O}{C}+0.0429\frac{N}{C}\right)
\end{equation}
Where LHV refer to lower heating value of fuel, C, H, O, N refer to mass fraction of carbon, hydrogen, oxygen, nitrogen by element analysis.
More details of power plant equipments' exergy  efficiency calculation can be found in Ref.~\cite{G2016Exergy}

In order to clearly analyze the effect of system optimization, this paper divides the double-reheat USC system into four main subsystems and a sum of all other equipments, valves and pips named "other".
The four main subsystems are: boiler with out APH, turbines, air preheat subsystem and regenerative subsystem.
The equations mentioned above can also be used into exergy analysis of these four main subsystems.
For the "other" part, this paper used counter balance analysis method to calculate its exergy destruction rate, which means subtract the share of the four main subsystems from the total exergy destruction.
The exergy destruction rate can be calculated by using equation as follows:

@@

\section{Thermodynamic performance evaluation} % (fold)
\label{sub:Thermodynamic_evaluation}
%对word版本的分布进行了较大的改动，需要继续调节
\subsection{Thermodynamic comparison in design condition}
\label{ssub:desing_compare}
%表四
The comparison of thermal dynamic performance between these two systems is given in Table~\ref{table:thermal performance compare}. 
Under design condition, the novel system brings an improvement of net generating power by 11.02 MW, and reduces SCE consumption by 5.5\,g/kWh.
The power generation efficiency reaches 48.73\%, and 1.04\% higher then that of reference system.
Meanwhile, the exergy efficiency of novel system is 1.01\% higher, showing good exergy-saving effect.
